### 2022-04-19 input/experiments.tex
Remove some stuff to cope with the 11 pages
very small space winning...

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another communication link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution.
%
To favor more concurrent operations, we voluntary set
weights and latency to different values: each link has a weight
between 5 and 15 set randomly using a uniform distribution. This
allows nodes to receive messages in a different order than their
respective shortest path generating more messages to reach consistent
partitioning.

@@

\subsection{Cross autonomous systems}
\begin{asparadesc}
\item[Objective:] Highlight the shortcoming of \NAME in
  infrastructures composed of multiple autonomous systems and
    discuss an improvement called \underline{cross} \underline{\NAME}
    (\NAMEC). At coarse-grained, \NAMEC enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the  additional two pages available in the
    camera-ready version of the article.} dynamic partitioning by
    allowing AS' gateways to stop notifications when their respective
    network does not appear to have a source.

@@

    \noindent Figure~\ref{fig:europe-ases} also highlights the worst
    case scenario of \NAME: the cost of France's \texttt{Add} is close
    to that of Portugal's \texttt{Add} since it updates the whole
    Europe excluding Portugal and Spain. On the opposite, \NAMEC only
    updates France's 39 \processes.

>>>>

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution.
%
To favor more concurrent operations, we voluntary set
weights and latency to different values: each link has a weight
between 5 and 15 set randomly using a uniform distribution. This
allows nodes to receive messages in a different order than their
respective shortest path generating more messages to reach consistent
partitioning.

@@

\subsection{Cross autonomous systems}
\begin{asparadesc}
\item[Objective:] Highlight the shortcoming of \NAME in
  infrastructures composed of multiple autonomous systems and
    discuss an improvement called \underline{cross} \underline{\NAME}
    (\NAMEC). At coarse-grained, \NAMEC enables
    \emph{lazy} %\footnote{Laziness properties and \NAMEC would be
    %    further detailed in the  additional two pages available in the
    %    camera-ready version of the article.}
    dynamic partitioning by
    allowing AS' gateways to stop notifications when their respective
    network does not appear to have a source.

@@

    \noindent Figure~\ref{fig:europe-ases} also highlights the worst
    case scenario of \NAME: the cost of France's \texttt{Add} is close
    to that of Portugal's \texttt{Add} since it updates the whole
    Europe excluding Portugal and Spain. Contrarily, \NAMEC only
    updates France's 39 \processes.

### 2022-04-19 input/figpartitionintuition.tex
wining space piece by piece
starting with xas, small changes here and there
very small space winning...

\begin{figure*}
\centering
\subfloat[\Process~$R$ efficiently advertises its content using epidemic propagation. Every \process requests $R$ if needed.\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-1.png}}
\hfill
\subfloat[\Process $G$ creates a second replica splitting the red set in two. \Processes request their closest replica host.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
\subfloat[\Process $B$ creates another replica. \Process~$B$ needs to notify only a small subset of \processes.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
\subfloat[\Process $G$ destroys its replica. \Processes that belong to its partition must find the closest partition they are in.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
%
\caption{The french RENATER topology. Partitions
  grow and shrink depending on creations and removals of
  replicas.} \label{fig:partition_intuition}
\end{figure*}

>>>>

\begin{figure*}[t]
\centering
\subfloat[\Process~$R$ efficiently advertises its content by epidemic propagation. Every \process requests $R$ if needed.\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.23\textwidth]{img/Dynamic-partitioning-1.png}}
\hfill
\subfloat[\Process $G$ creates a second replica splitting the red set in two. \Processes request their closest replica host.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.23\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
\subfloat[\Process $B$ creates another replica. \Process~$B$ needs to notify only a small subset of \processes.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.23\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
\subfloat[$G$ destroys its replica. \Processes that belonged to its partition must find the closest partition they are in.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.23\textwidth]{img/Dynamic-partitioning-4.png}}
%
\caption{% The french RENATER topology.
  Partitions
  grow and shrink depending on creations and removals of
  replicas.} \label{fig:partition_intuition}
\end{figure*}
